\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\title{Sprint meeting}
\author{Starship Troopers}
\date{\today}

\begin{document}

\maketitle

\section*{Members present}
\begin{itemize}
\item Joshua Lee (engineer/tester)
\item Eoin Lernihan (engineer/tester)
\item David Newman (product owner)
\item Kevin Maloney (scrum master)
\end{itemize}

\section*{Process}
The sprint planning took place across two in-person team meetings
which occurred on the 17th of February and the 19th of February.
The first meeting saw the product owner begin drawing up the release
plan and organising the user stories to facilitate that process. The
team collectively performed a final review of the user story sizing to
ensure they were as accurate as possible before the sprint began.

The second meeting was occupied by the drawing up of the release plan
itself. The product owner and the scrum master used a large whiteboard to
perform this process. The team had unanimously agreed that a whiteboard
would provide the most expressive visual imagery to boost our team's
productivity, an idea we borrowed from Uzility\textregistered\ (check
out \texttt{uzility.com} for more fantastic agile ideas).

The product owner and scrum master ordered the chosen user stories by
priority. Each sprint was allocated a mean number of 25 user points, a
number that the team felt confident that we could complete within a
time-boxed two-week sprint.



\end{document}